\documentclass[parskip=half]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman,english]{babel}
\usepackage{lmodern}
\usepackage[juratotoc]{scrjura}
\usepackage[margin=2cm]{geometry}
\usepackage{digsig}
\makeatletter 
\renewcommand*{\parformat}{% 
	\global\hangindent 2em 
	\makebox[2em][l]{(\thepar)\hfill}\hspace{-0,3cm} 
} 
\makeatother 

\begin{document} 
\addchap{Publication of an image as part of this project}
With this document I confirm to the OpenMTLcalendar project and possible successor projects and the companies that want to print, distribute and use the OpenMTLcalendar that the image and myself meet the following criteria. These points serve as a basis for legal protection and reduction of effort.
\begin{contract}
	\Paragraph{title={Valid law}}
	I confirm that my image does not violate valid law and CC-BY-SA. I understand that this document is only to be understood as a supplement and safeguard. I am aware that penalties may be levied against me by violating laws and licenses. 
	Therefore, I do my best to protect the project and myself from penalties and abide by the law.
	
	\Paragraph{title={Author}}
	I am the author or photographer of the submitted image or artistic representation. I have not taken the picture on behalf of a company, organization or other legal person. Furthermore, I have not granted any company, organization or other legal entity exclusive rights to this image.
	
	\Paragraph{title={Use of the image}}
	I am aware that the work of this project is under CC-BY-SA license. Using the image does not give me any financial advantage and others may well pursue a profit-making intention with it without my objection. Under the conditions mentioned in the license, this can also be done in other projects.
	
	\Paragraph{title={Attribution}}
	I am aware that my full name or a pseudonym is required for any use of my submitted image. This results from the project license selection. In the process of image transmission, I will provide this information. A name change is not possible through the history in the version management. In addition, it is difficult to determine whether a person is still the same, since we do not have any identity features. Even a key for the digital signature can be stolen. I am aware that the project therefore refrains from subsequent name changes.
	
	\Paragraph{title={12 months agreement}}
	I am aware that a year has only 12 months. Therefore, my contribution is not visible in every calendar. I am also aware that the displays used can be changed at any time. The assignment of the months to the images is also unrestricted. My permission is not needed for removing, moving and using the image. I also do not expect any communication about it.
	
	\Paragraph{title={Freedom of panorama}}
	I confirm to the project that my contribution was made in public space. Public are all places that can be entered without access restrictions. Likewise, I did not use ladders or drones for the photo.
	In addition, the main object in the picture is permanent in this place.
	
	\Paragraph{title={People}}
	Even though there is a gray area in German law for photographing large crowds, I did my best not to photograph anyone recognizable. Furthermore, I confirm that \textbf{no children} are visible on the picture.
	
	\Paragraph{title={Signature}}
	The document offers the possibility of a digital signature. I use this function or another way to express my will and consent.
	
	\begin{Form}
		\digsigfield{5cm}{3cm}{My signature}
	\end{Form}
	
\end{contract}
\end{document}